---
title: "PROJECT2"
output: "github_document"
---
## Code for reading in the dataset and/or processing the data
```{r,echo=TRUE}
Steps<-read.csv("C:/Users/binay/OneDrive/Desktop/activity.csv")
Steps
```
## Histogram of the total number of steps taken each day
```{r,echo=TRUE}
totalsteps<-aggregate(Steps$steps,by=list(Steps$date),sum)
totalsteps
library(ggplot2)
colnames(totalsteps)=c("Date","STEPS")
g<-ggplot(totalsteps,aes(STEPS))+geom_histogram(,binwidth=1000)+xlab("steps")+ylab("frequency")
print(g)
```
## Mean and median number of steps taken each day
```{r,echo=TRUE}
meanstepsperday<-mean(totalsteps$STEPS,na.rm=TRUE)
meanstepsperday
medianstepsperday<-median(totalsteps$STEPS,na.rm=TRUE)
medianstepsperday
```
## Time series plot of the average number of steps taken
```{r,echo=TRUE}
timeseriessteps<-aggregate(steps~interval,Steps,FUN = mean,na.action = na.omit)
library(ggplot2)
m<-ggplot(timeseriessteps,aes(interval,steps))+geom_line(col="blue")+ggtitle("Time series plot")+xlab("interval")+ylab("steps")
print(m)
```
## The 5-minute interval that, on average, contains the maximum number of steps
```{r,echo=TRUE}
library(dplyr)
gg<-tbl_df(timeseriessteps)
gg %>% select(interval,steps)%>%filter(steps==max(timeseriessteps$steps))
```
## Code to describe and show a strategy for imputing missing data and Histogram of the total number of steps taken each day after missing values are imputed
```{r,echo=TRUE}
library(dplyr)
Nomissingsteps<-Steps[complete.cases(Steps),]
totalsteps1<-aggregate(Nomissingsteps$steps,by=list(Nomissingsteps$date),sum)
library(ggplot2)
f<-ggplot(totalsteps1,aes(x))+geom_histogram(,binwidth = 1000)+xlab("steps")+ylab("frequency")
print(f)
```
```{r,echo=TRUE}
MEAN<-mean(Nomissingsteps$steps)
MEAN
MEDIAN<-median(Nomissingsteps$steps)
MEDIAN
```
## Panel plot comparing the average number of steps taken per 5-minute interval across weekdays and weekends         
```{r,echo=TRUE}
Steps$day<-weekdays(as.Date(Steps$date))
Steps$weekdaytype<-ifelse(Steps$day=="Saturday"|Steps$day=="Sunday","weekend","weekday")
Steps$weekdaytype
```
```{r,echo=TRUE}
library(dplyr)
timeseriesstepzs1<-aggregate(steps~interval+weekdaytype,Steps,FUN = mean)
library(ggplot2)
a<-ggplot(timeseriesstepzs1,aes(interval,steps))+geom_line(col="blue")+facet_grid(weekdaytype~.)+xlab("5min Interval")+ylab("Steps")
print(a)
```
